sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-02-07 doc/paper-jss/owls.Rmd
Add CBC data note

This appendix illustrates the fitting of a model with a spatially varying coefficient for the effect a regional climate index on species count data using \pkg{sdmTMB}. 
We will use counts of Snowy Owls (*Bubo scandiacus*) observed in North America during annual Christmas Bird Counts [CBCs, @cbc]. 
Each survey is conducted between December 14 to January 5 in a 24.14 kilometer (15 mile) diameter circle. 
Circle locations are chosen by local volunteers and therefore reflect both locations of higher human densities and known bird watching locations.
Each circle (given a unique ID) is generally surveyed annually by at least 10 volunteers, or deemed inactive. 
While these locations are not random, the consistent sampling through time still make them useful for exploring spatiotemporal processes.

>>>>

This appendix illustrates the fitting of a model with a spatially varying coefficient for the effect a regional climate index on species count data using \pkg{sdmTMB}. 
We will use counts of Snowy Owls (*Bubo scandiacus*) observed in North America during annual Christmas Bird Counts [CBCs, @cbc].

All requests for use of Christmas Bird Count data must be [submitted to Audubon](https://survey123.arcgis.com/share/7dc33b4fff77468a8bba855291f86527) and must adhere to the [Audubon Policy Regarding use of Christmas Bird Count Data](https://www.audubon.org/content/policy-regarding-use-christmas-bird-count-data). Questions can be directed to `cbcadmin@audubon.org`.

Each survey is conducted between December 14 to January 5 in a 24.14 kilometer (15 mile) diameter circle. 
Circle locations are chosen by local volunteers and therefore reflect both locations of higher human densities and known bird watching locations.
Each circle (given a unique ID) is generally surveyed annually by at least 10 volunteers, or deemed inactive. 
While these locations are not random, the consistent sampling through time still make them useful for exploring spatiotemporal processes.
